Short-time expansion of Heisenberg operators in open collective quantum spin systems

### 2019-12-06 soc_squeezing/collective_paper/review/response.tex

  \green{We note that particle loss is an important decoherence
    mechanism in many experimental realizations of collective spin
    models[41].  In principle, a spin model has no notion of the
    particle annihilation operators that generate particle loss, and
    therefore cannot capture this effect directly.  Nonetheless, for a
    system initially composed of $N$ particles, the effect of particle
    loss can be emulated with $O(1/N)$ error by the dissipator
    $\check\D_{\t{loss}}$ defined by
    $\check\D_{\t{loss}}\hat\S_{\v m}=-\abs{\v m}\hat\S_{\v m}$, where
    $\abs{\v m}\equiv\sum_\alpha m_\alpha$ (see Appendix H).
    Furthermore, the effect particle loss can be accounted for exactly
    by (i) introducing an additional index on spin operators,
    $\hat\S_{\v m}\to\hat\S_{N\v m}$, to keep track of different
    sectors of fixed particle number within a multi-particle Fock
    space, and (ii) constructing jump operators that appropriately
    couple spin operators within different particle-number sectors.
    We defer a detailed exact accounting of particle loss to future
    work.}

  The new appendix provides mathematical justification for our claim
  that the dissipator $\check\D_{\t{loss}}$ emulates particle loss
  with $O(1/N)$ error.  We hope that these additions do a satisfactory
  job of addressing particle loss.

  As a last point, concerning the number of references in our work to
  past studies about the influence of decoherence on spin squeezing in
  the one-axis twisting (OAT) model: the small number of such
  references is due to the fact that we do not have any particular
  discussions of the influence of decoherence on spin squeezing with
  OAT, and do not consider such discussions relevant to our current
  work.  Even with decoherence (of the types considered in our work),
  the OAT model is an exactly analytically solvable (see
  \url{https://doi.org/gcsjdp}).  Approximate numerical methods such
  as that presented in our manuscript are therefore inappropriate
  tools for the study of OAT.  The primary role of OAT in our work is
  to serve as a simple and exactly solvable benchmark of our numerical
  methods, rather than an object of study in and of itself.  To
  clarify this point, we have changed the second paragraph of section
  III on spin squeezing, benchmarking, and breakdown (top of page 4),
  from:

  \red{Note that the OAT model is a special case of the zero-field
    Ising model, whose quantum dynamics admits an exact analytic
    solution even in the presence of decoherence[62].  We will
    benchmark our calculations using these analytical OAT results
    wherever applicable (see Appendix J, as well as the Supplementary
    Material of Ref.~[14]).}

  to:

  \green{Note that the OAT model is a special case of the zero-field
    Ising model, whose quantum dynamics admits an exact analytic
    solution even in the presence of decoherence[64].  The approximate
    and numerics-oriented TST expansion is therefore ill-suited for
    studying the OAT model, which will merely serve as an exactly
    solvable benchmark of our methods.  Wherever applicable, we will
    provide exact results for the OAT model (see Appendix K, as well
    as the Supplementary Material of Ref.~[14]).}

  We hope that the referee and editors understand our position on this
  matter -- namely, that we would rather avoid adding spurious
  references to past works on a subject (the influence of decoherence
  on spin squeezing in the exactly solvable OAT model) that is of
  little relevance to our work on a numerical method to compute spin
  correlators.

\item Concerning the final question, about the robustness of the TNT
  model:

  \blue{3. I am surprised by the results from the strong decoherence
    regimes in Fig.~2, which shows that twist and-turn (TNT) model is
    much more robust than OAT and TAT. Is this physical or just an
    artifact from numerical errors. To rule out the latter, I suggest
    the authors check the results in the strong decoherence regime by
    studying a smaller system, where Monte Carlo simulation is
    accessible and can be used as a comparison. If this result is
    indeed physical, if would be very helpful if the authors could
    comment on the reason?}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Miscellaneous changes}

\begin{enumerate}
\item In our discussions about the breakdown of the TST expansion in
  Sections II and III, we use the word ``unphysical'' to essentially
  mean ``not physically possible''.  In Section I, meanwhile, we
  comment about a method of simulation called the cumulant expansion,
  which breaks down in the presence of genuinely multi-body
  correlations.  In such a case, the cumulant expansion yields results
  that are {\it physically possible}, but {\it incorrect}.  For
  consistent use of language, we have therefore changed the following
  sentence in section I (bottom right of page 1):

  \red{The growth of genuinely multi-body correlations, however,
    eventually causes the cumulant expansion to yield unphysical
    results with no clear signature of failure.}

  to:

  \green{The growth of genuinely multi-body correlations, however,
    eventually causes the cumulant expansion to yield incorrect
    results with no clear signature of failure.}

\item One of our previous changes to the manuscript defined
  ``\green{$\abs{\v m}\equiv\sum_\alpha m_\alpha$}'' (bottom of page 2
  in the new text).  We have therefore removed a subsequent definition
  of this notation, which previously appeared in the following
  paragraph, ``\red{where
    $\abs{\v\ell}\equiv\sum_\alpha\ell_\alpha$}'' (middle right column
  of page 2 in the old text).

\end{enumerate}

\end{document}
